Versioned data: why it is needed and how it can be achieved (easily and cheaply)

### 2017-10-17 ms.tex
commenting out table 5 as it is not referenced in text - we already have plenty of tables as it is

\begin{table}[h!]
\centering
\caption{Alternative platforms for minting \textsc{doi}s from \texttt{GitHub} repositories.}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{4cm}p{8cm}}
  \hline
  \textbf{Provider} & \textbf{Features} \\ \hline
  \texttt{Zenodo}: \smurl{zenodo.org} & Automated \textsc{doi} for each \texttt{GitHub} release \\
    & Funded and maintained by CERN and OpenAIRE for long term preservation \\
    & At present, can only archive files embedded directly in the \texttt{git} repo, not produced by it as outputs\\
  \texttt{FigShare}: \smurl{figshare.com} & Builds data package based on \texttt{GitHub} release \\
    & Allows you to upload additional files, e.g. datasets built by code \\
    & Integrated with several journals, e.g. Nature family, \textsc{PNAS} \\
  \hline
  \end{tabular}
  }
\label{tab:doi_minting}
\end{table}

>>>>

%\begin{table}[h!]
%\centering
%\caption{Alternative platforms for minting \textsc{doi}s from \texttt{GitHub} repositories.}
%{\footnotesize
%\vspace{1cm}
%  \begin{tabular}{p{4cm}p{8cm}}
%  \hline
%  \textbf{Provider} & \textbf{Features} \\ \hline
%  \texttt{Zenodo}: \smurl{zenodo.org} & Automated \textsc{doi} for each \texttt{GitHub} release \\
%    & Funded and maintained by CERN and OpenAIRE for long term preservation \\
%    & At present, can only archive files embedded directly in the \texttt{git} repo, not produced by it as outputs\\
%  \texttt{FigShare}: \smurl{figshare.com} & Builds data package based on \texttt{GitHub} release \\
%    & Allows you to upload additional files, e.g. datasets built by code \\
%    & Integrated with several journals, e.g. Nature family, \textsc{PNAS} \\
%  \hline
%  \end{tabular}
%  }
%\label{tab:doi_minting}
%\end{table}

%\newpage
